---
title: "Peer Assessment 1"
output: html_document
---
##Loading and preprocessing the data

The data is a csv file that was downloaded and unzipped as activity.csv



```{r,echo = TRUE}
activity=read.csv('activity.csv')
```

What is mean total number of steps taken per day?


```{r, echo=TRUE}
hist(aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)$steps,xlab ="Days",main="Histogram")

barplot(aggregate(steps ~ weekdays(as.Date(date)), data = activity, sum, na.rm = TRUE)$steps, names.arg=c("Sunday", "Monday", "Tuesday", "Wednes", "Thuday",     "Friday", "Saturday"),main="Barplot",ylab = "Frequency")



#plot(steps, border = "dark blue", col = "light blue",main = "Number of Steps Per Day", xlab ="steps")
```


The mean and median total number of steps taken per day  

```{r,echo=TRUE}
tot<- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
 mean(tot$steps)
 
 median(tot$steps)
```

What is the average daily activity pattern?

```{r,echo=TRUE}

stpInt <- aggregate(steps ~ interval, data = activity, mean, na.rm = TRUE)
plot(steps ~ interval, data = stpInt, type = "l")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r,echo=TRUE}
maxIndex<-which.max(stpInt$steps)
stpInt[maxIndex,]$interval

```


Inputting missing values

```{r,echo=TRUE}
sum(is.na(activity$steps))
missingValues<-sum(is.na(activity$steps))

```
Number of missing rows is:`missingValues`

Strategy for filling in all of the missing values in the dataset: Find averages by day of week and time of day and replace the missing values with them.
```{r,echo=TRUE}
activity$day<- weekdays(as.Date(activity$date))
aggregatedLookupSet<-aggregate(steps ~ interval+day,data = activity, mean, na.rm = TRUE)

lookUp <- function(interval,day) {
    aggregatedLookupSet[aggregatedLookupSet$interval == interval & aggregatedLookupSet$day ==day, ]$steps
}

count <- 0 
for (i in 1:nrow(activity)) {
    if (is.na(activity[i, ]$steps)) {
        activity[i, ]$steps <- lookUp(activity[i, ]$interval,activity[i, ]$day)
        count = count + 1
    }
}
```

Total Number of Repaired Records: `Count`

Histogram Mean and Median are as below

```{r,echo=TRUE}
totalStp <- aggregate(steps ~ date, data = activity, sum)
hist(totalStp$steps)
mean(totalStp)
median(totalStp$steps)
```


Are there differences in activity patterns between weekdays and weekends?


```{r,echo=TRUE}
activity$day <- ifelse(as.POSIXlt(as.Date(activity$date))$wday ==0 | as.POSIXlt(as.Date(activity$date))$wday ==6, "weekend", "weekday")

activity$day <- factor(activity$day, levels = c("weekday", "weekend"))
stpInt2 <- aggregate(steps ~ interval + day, activity, mean)
library(lattice)
xyplot(steps ~ interval | factor(day), data = stpInt2, aspect = 1/2, type = "l")
```
