---
title: "Peer Assessment 1"
output: html_document
---
##Loading and preprocessing the data

The data is a csv file that was downloaded and unzipped as activity.csv



```{r,echo = TRUE}
activity=read.csv('activity.csv')
```

What is mean total number of steps taken per day?


```{r, echo=TRUE}
steps <- hist(aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)$steps)
plot(steps, border = "dark blue", col = "light blue",main = "Number of Steps Per Day", xlab ="steps")
```


The mean and median total number of steps taken per day  

```{r,echo=TRUE}
tot<- aggregate(steps ~ date, data = activity, sum, na.rm = TRUE)
 mean(tot$steps)
 
 median(tot$steps)
```

What is the average daily activity pattern?

```{r,echo=TRUE}

stpInt <- aggregate(steps ~ interval, data = activity, mean, na.rm = TRUE)
plot(steps ~ interval, data = stpInt, type = "l")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r,echo=TRUE}
maxIndex<-which.max(stpInt$steps)
stpInt[maxIndex,]$interval

```
Inputting missing values
Number of missing rows are:
```{r,echo=TRUE}
sum(is.na(activity$steps))

```
